An efficient composition of bidirectional programs by tupling and lazy updates

### 2020-02-21 paper/7.conclusion.tex
fixed based on Prof. Hu's comment
removing comma before because

We will continue our work on the following four points.
First is overcoming our limitation in $xpg$. In $xpg$, there are two limitations: only for very-well-behaved programs and restriction for $\pginline{Case}$ in Section~\ref{sect:pg}. To be a practical evaluation method, an extension of the target language is needed. After extension of the language, we can evaluate more various programs for experimental results.
Second is introducing an automatic analysis about BX programs and inputs to choose the best evaluation method.
Currently, programmers have to choose the evaluation method by themselves based on their BX programs and inputs. If this analysis is achieved, we can reduce programmers' burden.
Third is introducing a type system to our target language, especially the datatype of sources and view. If we introduce this, we can avoid runtime errors like statically-typed functional languages. For this, we need to investigate more about \textcolor{red}{how to construct dummy values}, because the current definition used in our experiments %Section~\ref{sect:experiments}
will cause type errors.
\textcolor{red}{Fourth is using a lazy language. Although we used a strict language OCaml in this paper, if we use a lazy language, we might skip one of the optimizations.}

>>>>

We will continue our work on the following four points.
First is overcoming our limitation in $xpg$. In $xpg$, there are two limitations: only for very-well-behaved programs and restriction for $\pginline{Case}$ in Section~\ref{sect:pg}. To be a practical evaluation method, an extension of the target language is needed. After extension of the language, we can evaluate more various programs for experimental results.
Second is introducing an automatic analysis about BX programs and inputs to choose the best evaluation method.
Currently, programmers have to choose the evaluation method by themselves based on their BX programs and inputs. If this analysis is achieved, we can reduce programmers' burden.
Third is introducing a type system to our target language, especially the datatype of sources and view. If we introduce this, we can avoid runtime errors like statically-typed functional languages. For this, we need to investigate more about \textcolor{red}{how to construct dummy values} because the current definition used in our experiments %Section~\ref{sect:experiments}
will cause type errors.
\textcolor{red}{Fourth is using a lazy language. Although we used a strict language OCaml in this paper, if we use a lazy language, we might get laziness for free.}
